---
title: "Prokect 4"
author: "Symphony Hopkins"
date: "2023-04-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Read the dataset in Batteries_Life.csv Download Batteries_Life.csv into R. Name the loaded data Batteries_Life. And use the head() function to show the first 6 rows.**

```{r, include = TRUE, echo = TRUE}
#importing dataset
Batteries_Life <- read.csv("~/Documents/Maryville_University/DSCI_618/Week 4/Batteries_Life.csv")

#displaying first 6 rows
head(Batteries_Life, 6)
```

**Conduct the analysis of variance and test hypotheses on the main effects. What conclusions can be drawn using significance level=0.05?**

```{r, include = TRUE, echo = TRUE}
#converting columns to factors
factors <- c('Brand','Device')
Batteries_Life[,factors] <- lapply(Batteries_Life[,factors], as.factor)

#two-way ANOVA model 
bl_two_way <- aov(Life ~ Brand + Device, data=Batteries_Life)
summary(bl_two_way)

```

The brand's p-value, 0.0112, is less than our significance level (=0.05), which means we can reject the null hypothesis and conclude that there is a significant difference in mean battery life due to brand type.

The device's p-value, 4.5e-07, is less than our significance level (=0.05), which means we can reject the null hypothesis and conclude that there is a significance difference in mean battery life due to device type.

Overall, we can conclude that the main effects, brand and device, are significant.

**Construct an interaction plot.**
```{r, include = TRUE, echo = TRUE}
#importing library
library(ggplot2)

#creating interaction plot
with(data = Batteries_Life, interaction.plot(Brand, Device, Life, type="b", pch=19, fixed=T,
                                             xlab='Brand', ylab='Mean Life',col=10:12))

```

The slopes of the lines appear slightly different (almost parallel but not exactly), so there may be a slight interaction; however, we would have to conduct a two-way ANOVA with interaction before making conclusions.

**Test on the interaction between factors. What conclusions can be drawn using significance level=0.05?**

```{r, include = TRUE, echo = TRUE}
#two-way ANOVA model with interaction
bl_two_way_ir <- aov(Life ~ Brand * Device, data=Batteries_Life)
summary(bl_two_way_ir)
```

Once again, we can see that brand and device type have p-values less than 0.05, so we can conclude that they have a significant effect on the difference in mean battery life. 

The p-value for the interaction between brand and device type is greater than our significance level (0.6430 > 0.05), so we can conclude that the interaction is not significant.

**Prepare appropriate residual plots and comment on the model’s adequacy.**

```{r, include = TRUE, echo = TRUE}
#checking model assumptions
opar <- par(mfrow=c(2,2),cex=.8)
plot(bl_two_way_ir)
```

For the residuals vs fitted plot, we don't see any non-linear patterns, so that is a good indication that we don't have any non-linear relationships. It appears that there a slightly larger variance in the larger fitted values. In the normal Q-Q plot, the points follow the diagonal line for the most part, so we can assume normality. However residual points 4, 7, and 8 seem to be extreme, so we may need to investigate the effects of these points. The Constant Leverage plot indicates this information as well. For the Scale-Location plot, the points are not equal spread so we cannot assume homoscedasticity.  

**Which brand of batteries would you recommend?**

From the interaction plot we created earlier, we saw that brand B had a higher life average compared to brand A, and we know that this difference in means is significant because of our findings from the two-way ANOVA test; so, we would recommend **brand B** batteries. 






